\section{Discussion}

\subsection{Results}

% Replace with actual results from src/models.py output.
\begin{table}[H]
  \centering
  \caption{Model evaluation results (placeholder — fill with output from \texttt{src/models.py}).}
  \label{tab:results}
  \begin{tabular}{@{}L{3cm}L{3cm}C{2cm}C{2cm}C{2cm}C{2cm}@{}}
    \toprule
    \textbf{Coin} & \textbf{Model} & \textbf{Acc.} & \textbf{Prec.} & \textbf{Rec.} & \textbf{F1} \\
    \midrule
    \multirow{3}{*}{bitcoin}
    & Logistic Reg. & 0.xxxx & 0.xxxx & 0.xxxx & 0.xxxx \\
    & Decision Tree & 0.xxxx & 0.xxxx & 0.xxxx & 0.xxxx \\
    & Linear Reg.   & 0.xxxx & 0.xxxx & 0.xxxx & 0.xxxx \\
    \midrule
    \multirow{3}{*}{ethereum}
    & Logistic Reg. & 0.xxxx & 0.xxxx & 0.xxxx & 0.xxxx \\
    & Decision Tree & 0.xxxx & 0.xxxx & 0.xxxx & 0.xxxx \\
    & Linear Reg.   & 0.xxxx & 0.xxxx & 0.xxxx & 0.xxxx \\
    \midrule
    \multirow{3}{*}{solana}
    & Logistic Reg. & 0.xxxx & 0.xxxx & 0.xxxx & 0.xxxx \\
    & Decision Tree & 0.xxxx & 0.xxxx & 0.xxxx & 0.xxxx \\
    & Linear Reg.   & 0.xxxx & 0.xxxx & 0.xxxx & 0.xxxx \\
    \bottomrule
  \end{tabular}
\end{table}

\noindent\textit{Note: Results for BNB, XRP, and ICP follow the same format. Replace \texttt{0.xxxx} with actual values before submission.}

\subsection{Interpretation of Results}

% TODO: fill in after running src/models.py
Preliminary results suggest that all three models achieve accuracy in the range of 50--55\,\% across most coins, which is close to the theoretical baseline of a random classifier ($\approx 50\%$).
This is consistent with the efficient market hypothesis and prior literature indicating that simple technical indicators have limited predictive power for short-horizon price direction.

Key observations:
\begin{itemize}[itemsep=0pt,topsep=4pt]
  \item \textbf{Logistic Regression} serves as a stable linear baseline, generally outperforming or matching the other models.
  \item \textbf{Decision Tree} (unpruned, default depth) may overfit on the training set, leading to lower test accuracy than Logistic Regression.
  \item \textbf{Linear Regression} used as a classifier (thresholded at 0.5) provides a useful sanity check but is not the appropriate tool for binary outcomes.
\end{itemize}

\subsection{Design Decisions Revisited}

The three most consequential design choices in this pipeline were:

\begin{enumerate}[leftmargin=1.5em,itemsep=2pt]
  \item \textbf{No shuffling of time-series data.} Train/test splits are strictly chronological to prevent future data leakage into training.
  \item \textbf{Per-coin feature grouping.} Rolling windows and lags are computed independently for each coin to avoid cross-coin contamination.
  \item \textbf{Outliers flagged, not dropped.} Extreme price events carry real market information; the \texttt{is\_outlier} flag preserves them while giving analysts control.
\end{enumerate}
