\section{Conclusion}

\subsection*{Summary and Learnings}

This project built a reproducible end-to-end pipeline from raw web scraping to binary classification
for cryptocurrency price-direction prediction.
The central finding is that publicly available daily market indicators have very limited predictive
power for next-day price direction.
Test-set accuracy for both models and all three coins is consistent with random-walk behaviour and
aligns with the theoretical ceiling derived from the ACF analysis.

Three methodological lessons stood out.
First, stationarity matters. Including non-stationary level features such as moving averages and
market capitalisation introduced spurious correlations that would have inflated reported performance.
Second, data leakage is easy to introduce in time-series settings. Initial experiments with unlagged
features produced 100\,\% Decision Tree accuracy, which immediately revealed the error.
Third, the EDA correctly predicted the performance range before any model was trained, demonstrating
that thorough exploratory analysis is a prerequisite for trustworthy modelling.

\subsection*{Limitations}

\begin{itemize}[itemsep=0pt,topsep=3pt]
  \item The feature set is limited to price-derived technical indicators. Sentiment data, on-chain
        metrics, and macroeconomic variables are excluded.
  \item Only two classifiers are evaluated. Ensemble methods such as Random Forest may offer marginal
        improvements without additional data.
  \item The Decision Tree is not hyperparameter-tuned. Pruning could reduce the gap between
        validation and test performance.
\end{itemize}

\subsection*{Outlook}

Future work could enrich the feature set with news sentiment or social media signals, apply
TimeSeriesSplit cross-validation for more robust model selection, or investigate whether
predictability increases over multi-day prediction horizons.
Extending the pipeline to additional coins would allow broader generalisations about market
efficiency across different asset classes.
